Observations

### 2020-05-02 exp_eth_val.Rmd
Add files via upload

```{r ethnicp, fig.pos="h!", out.width="98%",fig.align='center',fig.show="hold", fig.cap="prep fig ethnic population", echo=FALSE, include=FALSE}

circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")
circle_minority.labs <-  c("20% \nMinority Circle", "50% \nMinority Circle","80% \nMinority Circle")
names(circle_minority.labs) <- c("20", "50","80")

mj_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .5:.5, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mj_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .8:.2, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mj_e20.png",mj_e20)
 ggsave("mj_m20.png",mj_m20)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mj_e20.png"),image_read("mj_m20.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "majo20.png", format = "png")

#

mj_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .5:.5, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mj_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .8:.2, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mj_e50.png",mj_e50)
 ggsave("mj_m50.png",mj_m50)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mj_e50.png"),image_read("mj_m50.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "majo50.png", format = "png")

#

mj_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .5:.5, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mj_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .8:.2, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mj_e80.png",mj_e80)
 ggsave("mj_m80.png",mj_m80)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mj_e80.png"),image_read("mj_m80.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "majo80.png", format = "png")

# minority

circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")
circle_minority.labs <-  c("20% \nMinority Circle", "50% \nMinority Circle","80% \nMinority Circle")
names(circle_minority.labs) <- c("20", "50","80")

mn_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .5:.5, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mn_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .8:.2, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mn_e20.png",mn_e20)
 ggsave("mn_m20.png",mn_m20)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mn_e20.png"),image_read("mn_m20.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "min20.png", format = "png")

#

mn_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .5:.5, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mn_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .8:.2, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mn_e50.png",mn_e50)
 ggsave("mn_m50.png",mn_m50)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mn_e50.png"),image_read("mn_m50.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "min50.png", format = "png")

#

mn_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .5:.5, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mn_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .8:.2, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mn_e80.png",mn_e80)
 ggsave("mn_m80.png",mn_m80)
# a <- image_r
#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mn_e80.png"),image_read("mn_m80.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "min80.png", format = "png")

@@

```{r sqro, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }

 circle_local.labs <- c("20% Circle \nMajority", "50% Circle \nMajority","80% Circle \nMajority")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Circle \nMinority", "50% Circle \nMinority","80% Circle \nMinority")
names(circle_minority.labs) <- c("20", "50","80")

sqroeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_or","Ethnic" = "eth_sq_or"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square orange, ethnic minority") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )

sqromj<- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_or","Ethnic" = "eth_sq_or"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square orange, ethnic minority") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )

 sqroeq
 sqromj
```

```{r crloA, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }

dataone$rev_circle_orange <- fct_rev(factor(dataone$circle_orange))

 circle_blue.labs <- c("20% Circle Blue", "50% Circle Blue","80% Circle Blue")
names(circle_blue.labs) <- c("20", "50","80")
 rev_circle_orange.labs <-  c("80% Circle \nOrange", "50% Circle \nOrange","20% Circle \nOrange")
names(rev_circle_orange.labs) <- c("80", "50","20")

crloeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(rev_circle_orange ~ circle_blue + segregation, labeller = labeller(rev_circle_orange = rev_circle_orange.labs, circle_blue = circle_blue.labs), switch  = "y") +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle orange, equal ethnic size") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
 crloeq

crlomj <- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle orange, ethnic minority") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )

@@

```{r sqrb, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }

 circle_local.labs <- c("20% Circle \nMajority", "50% Circle \nMajority","80% Circle \nMajority")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Circle \nMinority", "50% Circle \nMinority","80% Circle \nMinority")
names(circle_minority.labs) <- c("20", "50","80")

sqrbeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_bl","Ethnic" = "eth_sq_bl"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square blue, equal ethnic size") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )

>>>>

dataone$rev_circle_orange <- fct_rev(factor(dataone$circle_orange))
dataone$rev_circle_blue <- fct_rev(factor(dataone$circle_blue))

datatwo$rev_beta_iv_circle <- fct_rev(factor(datatwo$beta_iv_circle))
datatwo$rev_beta_ie_square <- fct_rev(factor(datatwo$beta_ie_square))

  rev_circle_blue.labs <- c("80% Circle \nBlue" ,"50% Circle \nBlue","20% Circle \nBlue")
names(rev_circle_blue.labs) <- c("80", "50","20")
 rev_circle_orange.labs <-  c("80% Circle \nOrange", "50% Circle \nOrange","20% Circle \nOrange")
names(rev_circle_orange.labs) <- c("80", "50","20")

 circle_blue.labs <- c("20% Circle \nBlue", "50% Circle \nBlue","80% Circle \nBlue")
names(circle_blue.labs) <- c("20", "50","80")
 circle_orange.labs <-  c("20% Circle \nOrange", "50% Circle \nOrange","80% Circle \nOrange")
names(circle_orange.labs) <- c("20", "50","80")

@@

```{r baselineone,fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap=" Baseline space", echo=FALSE, include=TRUE  }

knitr::include_graphics("baseline_1.png")

```{r crlo,fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, first section", echo=FALSE, include=TRUE  }

crloeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(rev_circle_orange ~ circle_blue + segregation, labeller = labeller(rev_circle_orange = rev_circle_orange.labs, circle_blue = circle_blue.labs), switch  = "y") +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle orange, equal ethnic size") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )

crlomj <- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(rev_circle_orange ~ circle_blue + segregation, labeller = labeller(rev_circle_orange = rev_circle_orange.labs, circle_blue = circle_blue.labs), switch  = "y") +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle orange, ethnic minority") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )

@@

```{r crlblmajority, fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="Circle in majority condition.", echo=FALSE, include=TRUE}

  rev_circle_blue.labs <- c("80% Circle \nBlue" ,"50% Circle \nBlue","20% Circle \nBlue")
names(rev_circle_blue.labs) <- c("80", "50","20")

 rev_circle_orange.labs <-  c("80% Circle \nOrange", "50% Circle \nOrange","20% Circle \nOrange")
names(rev_circle_orange.labs) <- c("80", "50","20")

dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_bl","Ethnic" = "eth_cl_bl"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid( rev_circle_blue  ~ circle_orange  + segregation, labeller = labeller(circle_orange =circle_orange.labs, rev_circle_blue = rev_circle_blue.labs), switch  = "y") +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle blue, ethnic majority") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )

```{r heatmapdsquare,fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Square orange, heterogenous preferences", echo=FALSE, include=TRUE }
